Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-03 manuscript/manuscript.tex
median section

@@

Then, we define a replicate covariance analog of $G$, $G_R$,

% \begin{align}

% \end{align}

@@

>>>>

\vb{One concern is that these covariances reflect a few large-effect loci
  rather than selection on a polygenic trait. Since our covariances are
  essentially averages over loci, the covariance estimate can be strongly
  affected by a single outlier region. To test whether large outlier regions
  drive the genome-wide signal we see in the \textcite{Barghi2019-qy} data, we
  calculate the covariances in 100kb windows along the genome (we refer to
  these as windowed covariances throughout) and exclude the upper and lower
  $\alpha$ tails to calculate the trimmed average windowed covariance. As
  $\alpha$ increases to 0.5, the trimmed covariance converges to the median
  windowed covariance (by the definition of the median; see Supplementary
  Figure \ref{suppfig:barghi-trimmed-mean}). In other words, this median
  windowed covariance is a measure of the genome-wide covariance robust to
  large-effect loci; we find that the median windowed covariance $\cov(\Delta
  p_0, \Delta p_{10})$ (pooling all replicates) is also significantly different
  from zero, 0.0016 (0.95\% CIS [0.0015, 0.0017]).

 }

@@

Then, we define a replicate covariance analog of $G$,

\begin{align}
  G_R(t) = \frac{\E_{A \ne B}(\sum_{i\ne j}^t \cov(\Delta p_{i,A}, \Delta p_{j,B}))}{\E_R(\var(p_{t,R} - p_{0,R}))}
\end{align}

where $\E_{A \ne B}$ indicates that the expectation is taken over all ordered
pairs of replicates (e.g. summing all off-diagonal elements replicate
covariances), and $\E_R$ indicates taking expectation over all replicates.

@@

\subsection{\textcite{Barghi2019-qy} Trimmed Window Covariances}

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/barghi-trimmed-mean.pdf}

  \caption{The genome-wide covariance ($\cov(\Delta p_0, \delta p_10)$ pooling
    all replicates) averaged (red line) and the median windowed covariance
    (blue) for the \textcite{Barghi2019-qy} dataset. The trimmed average window
    covariance, excluding the $\alpha$ lower and upper tails, converges to the
     median windowed covariance. This indicates that genome-wide covariance are
     not being overly dominated by a large-effect loci in few windows.}

  \label{suppfig:barghi-trimmed-mean}
\end{figure}
